Presentation: OPX

### 2022-08-03 Presentasjon/Presentasjon v3.Rmd
Presentasjon foreløpig

---
title: "Presentasjon OPX Fiffig tittel"
author: "Group 5: Aga, Amalie, Henrik, Ida, Torbjørn"
date: "2022-08-04"
output: 
  ioslides_presentation:
    widescreen: TRUE 
    css: stylesss.css
---

@@

## <br> Phase 1 – how to harvest and analyze the data?
- OPX wanted us to harvest data --> how? <br> 
- A webcrawler? <br> 
No: Would not work for every organization 
- A code that could read PDF? <br> 
Perhaps: Financial statements as text tables and as images

## <br> Phase 2 – Exploring three options
- 1. Reading PDFs <br>
Issue: Not always published as text
- 2. Webscraping from Proff.no <br>
Issue: Proff.no does not allow webscraping
- 3. Webscraping the Brønnøysund registry <br>
Issue: No API access, and access costs ~ kr 500K

## <br> Workarounds... 
- Proff.no: Download HTML?
- Brønnøysund: Request temporary access

## <br> ... and why they did not work
- Different accounting items used
- Incomplete financial reporting from NGOs

@@

## <br> Which led us to Phase 3 – Scrapping the scraping
- OPX wanted KPIs
- Found useful KPIs
- Created an interactive dashboard

## <br> Data collection & data description
- Used data from OPX and Proff.no 
- OPX: From their webpage
- Used to create KPIs and check our codes
- Proff.no: Downloaded HTML documents
- Used to create visualizations

@@

@@

## <br> Our experience
- Unsolvable case due to non-existent data
- Hard to create credible KPIs due to limited knowledge of economics and the NGO sector
- **Insight into real-life work challenges - the clash between what is desired and what is possible**

>>>>

---
title: "Presentation: OPX"
author: "Group 5: Aga, Amalie, Henrik, Ida, Torbjørn"
date: "2022-08-04"
output: 
  ioslides_presentation:
    widescreen: TRUE 
    css: stylesss.css
---

@@

## <br> How to harvest and analyze the data?
- OPX wanted data collection to be automated <br> 
- Webscraping? <br> 
No: Different HTML and PDF structures
- A code that could read PDF documents? <br> 
Perhaps: Financial statements as text tables and as images

## <br> Exploring three options
- 1. Reading PDFs <br>
Issue: Not always published as text
- 2. Webscraping from Proff.no <br>
Issue: Proff.no does not allow (automated) webscraping
- 3. Webscraping the Brønnøysund registry <br>
Issue: No API access, and access costs ~ NOK 500 000

#BYTTE UT MED 1 2 3

## <br> Workarounds... 
- Proff.no: Download the webpage as HTML document?
- Brønnøysund: Received XML files from Statistics Norway

## <br> ... and why they did not work
- XML not a viable long term solution for OPX 
- Incomplete financial reporting from NGOs -- no legal obligations
- Proff.no vs. OPX: Different accounting items used <br> <br> <br>

```{r, out.height="188", out.width="500", fig.align='center'}
knitr::include_graphics("Images/FRI.png")

@@

## <br> Which led us to scrapping the scraping <br>
- Found useful KPIs
- Created an interactive dashboard

## <br> Data collection & data description
- Proff.no: Downloaded HTML documents <br>
Used to create visualizations
- OPX: From their webpage <br>
Used to create KPIs and test our codes

@@

## <br> <br> <br> <br> torbjornso.shinyapps.io/NGOanalysis/

@@

## <br> Our experience
- Unsolvable case due to lack of accessible and relevant data
- Hard to create credible KPIs due to limited knowledge of economics and the NGO sector
- **Insight into real-life work challenges - the clash between what is desired and what is possible**
